Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Publication year") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count frequency (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

  #brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
  brs <- seq(min(dfm$date), max(dfm$date), 10)

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=brs, labels = insert_minor(brs, 2))
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
  print(p)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 5)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +
     xlab("Publication year") +
     ylab("Title count (n)")

@@

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df00 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat) %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
                 mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

@@

df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
df$publication_place <- droplevels(factor(df$publication_place))

@@

   p <- ggplot(dfss,
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      scale_fill_stata() +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
      #scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +                 
       ylab("Title count (n)") +
       xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) + 
       scale_color_stata() +
       ggtitle(catalogue)       
  print(p)
```

>>>>

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Publication year") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

  #brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
  brs <- seq(min(dfm$date), max(dfm$date), 10)
  brsy <- seq(0, round(max(dfm$Documents), -2), 250)

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=brs, labels = insert_minor(brs, 2))
  p <- p + scale_y_continuous(breaks=brsy, labels = brsy)  
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
  print(p)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 5)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(paste("Unique publishers (", catal, ")", sep = ""))

@@

brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 1)

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +
     xlab("Publication year") +
     ylab("Title count (n)")

@@

# Take cities from Fennica for Turku
cat <- "Fennica"

df2 <- df00 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat) %>%
	       group_by(publication_decade, publication_place)

df2$publication_place[!df2$publication_place == "Stockholm"] <- "Other"
df2$publication_place <- droplevels(factor(df2$publication_place))

df2 <- df2 %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
                 mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

@@

@@

   p <- ggplot(dfss,
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Publication year") +
      ylab("Title count (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      scale_fill_stata() +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
      #scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
       ylab("Title count (n)") +
       xlab("Year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = 1600)) +
       scale_y_continuous(label = scientific_10) + 
       scale_color_stata() +
       ggtitle(catalogue)       
  print(p)
```
